\textbf{Real-time guitar transcription using\\Fourier transform based methods}\\A pitch estimation framework and overtone sieve algorithm

### 2021-04-13 paper.tex
nog verder af

\title{\textbf{Multi-pitch estimation based on mathematical models}\\A pitch estimation framework and harmonic overtone sieve algorithm}
\author{Luc de Jonckheere}
% \date{}

@@

\subsection{Polyphonic performance: intervals}
To test the polyphonic performance of our system, we let it determine the played notes in an interval. We play every interval within an octave to test if there are any problems with separating the notes in specific intervals. For instance, some interference may cause oscillating peaks in the frequency domain. Again, we try all the intervals at different root notes, as especially for intervals the pitch of the root note may make a big difference. As we mentioned before, when two peaks are too close together, we cannot distinguish them. Often, the second note is distinguished an octave higher. In Table~\ref{tab:polperf} is a summary of the results. Here, we list the number of semitones $n$ between the two notes in an interval, if both notes were correctly found. If not, we denote if the second note was detected an octave higher. This often happens, because we cannot distinguish two notes in small intervals at low pitches. The last column shows if there were other notes reported which were not transients.
\begin{table}[H]%\vspace{-3mm}
    \centering
    \begin{tabular}{r|rrr}
        $n$ & both & octave & other \\
        \hline
        1  &  &  &  \\
        2  &  &  &  \\
        3  &  &  &  \\
        4  &  &  &  \\
        5  &  &  &  \\
        6  &  &  &  \\
        7  &  &  &  \\
        8  &  &  &  \\
        9  &  &  &  \\
        10 &  &  &  \\
        11 &  &  & 
    \end{tabular}
    \caption{Performance of distinguishing notes in an interval with root note $\text{A}_2$.}
    \label{tab:polperf}
\end{table}\vspace{-3mm}
In the tables, we can see that... (not enough overtones for low pitched intervals...)

>>>>

\title{\textbf{Real-time guitar transcription using\\Fourier transform based methods}\\A pitch estimation framework and overtone sieve algorithm}
\author{Luc de Jonckheere}
% \date{}

@@

\subsection{Polyphonic performance: intervals}
To test the polyphonic performance of our system, we let it determine the played notes in an interval. We play every interval within an octave to test if there are any problems with separating the notes in specific intervals. For instance, some interference may cause oscillating peaks in the frequency domain. Again, we try all the intervals at different root notes, as the pitch of the root note may make a big difference in performance. As we mentioned before, when two peaks are too close together, we cannot distinguish them. Often, the second note is distinguished an octave higher. We set the overtone error threshold to 10 cents. This is a relatively small value, but this allows us to see small problems in our algorithms better. Furthermore, as described in~\ref{sec:future}, we should not use a constant value, but use a different value for every $n$-th overtone. In Tables~\ref{tab:polperf1}--\ref{tab:polperf3} is a summary of the results. Here, we list the number of semitones $n$ between the two notes in an interval, if both notes were correctly found. If not, we denote if the second note was detected an octave higher. This often happens, because we cannot distinguish two notes in small intervals at low pitches. The last column shows if there were other notes reported which were not transients.
\begin{table}[H]\vspace{-4mm}
    \centering
    \begin{tabular}{r|lll}
        $n$ & both & octave & other \\
        \hline
        1  & false & true & 1-3 slightly inharmonic overtones \\
        2  & false & false & - \\
        3  & false & true & $\text{C}_4$ and $\text{G}_4$ (+ random at start) \\
        4  & true & - & Sometimes octave instead\\ &&& and 1-2 inharmonics at start \\
        5  & true & - & 1 slightly inharmonic overtone \\
        6  & true & - & 1-3 slightly inharmonic overtones \\
        7  & true & - & no \\
        8  & true & - & no \\
        9  & true & - & occasional inharmonic overtone \\
        10 & true & - & 1-2 slightly inharmonic overtones \\
        11 & true & - & 1-2 slightly inharmonic overtones
    \end{tabular}
    \caption{Performance of distinguishing notes in an interval with root note $\text{A}_2$.}
    \label{tab:polperf1}
\end{table}\vspace{-3mm}
\begin{table}[H]%\vspace{-3mm}
    \centering
    \begin{tabular}{r|lll}
        $n$ & both & octave & other \\
        \hline
        1  & false & true & about 4 slightly inharmonic overtones \\
        2  & false & true & about 4 slightly inharmonic overtones \\
        3  & true & - & $\text{C\#}_6$ or $\text{E}_6$ in first few frames \\
        4  & true & - & no \\
        5  & true & - & no \\
        6  & true & - & no \\
        7  & true & - & no \\
        8  & true & - & random note 3 times \\
        9  & true & - & no \\
        10 & true & - & no \\
        11 & true & - & no
    \end{tabular}
    \caption{Performance of distinguishing notes in an interval with root note $\text{A}_3$.}
    \label{tab:polperf2}
\end{table}\vspace{-3mm}
\begin{table}[H]%\vspace{-3mm}
    \centering
    \begin{tabular}{r|lll}
        $n$ & both & octave & other \\
        \hline
        1  & false & true & occasional $\text{E}_6$ \\
        2  & true & - & no \\
        3  & true & - & no \\
        4  & true & - & no \\
        5  & true & - & no \\
        6  & true & - & no \\
        7  & true & - & no \\
        8  & true & - & no \\
        9  & true & - & no \\
        10 & true & - & no \\
        11 & true & - & no
    \end{tabular}
    \caption{Performance of distinguishing notes in an interval with root note $\text{A}_4$.}
    \label{tab:polperf3}
\end{table}\vspace{-3mm}
In the tables, we can see that the algorithm performs well on higher pitched intervals. On medium pitched intervals, the small intervals become more of a problem, but most intervals are detected correctly. Transients are however visible for longer in the small intervals. Big problems arise when we look at the lower pitched intervals. There is much noise in the results and many slightly inharmonic overtones are reported. These could be filtered out by increasing the overtone error threshold, but that does not solve the overtones being inharmonic. The inharmonic overtones are less of a problem for larger intervals.

% We also look at the percentage of overtones that is filtered throughout a recording of an interval.
As the harmonic overtone sieve algorithm is only a proof of concept, absolute performance measurements will yield bad results. By measuring the performance relative to having no filtering, we can show the effectiveness of our algorithm. This is done by measuring the percentage of overtones that is filtered throughout a recording of an interval. TODO: See Figure~\ref{fig:relative} for some examples of
